SDR enhancement by clouds

### 2024-04-06 article/article.Rmd
Commit 2024-04-06 18:14

```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
knitr::include_graphics("../images/P_energy-6.png")
```
Subsequently, the total annual energy observed during CE events shows an increase of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.

>>>>

```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly CE number of occurancies."}
knitr::include_graphics("../images/P_energy-6.png")
```

Subsequently, the mean annual increase of energy due to CE events is
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.
